
\bibitem[Anderson, 2000]{Anderson2000:Slowboats}
Anderson, A. (2000).
\newblock Slow boats from china: issues in the prehistory of indo-pacific
  seafaring.
\newblock In O'Connor, S. and Veth, P., editors, {\em East of Wallace's Line:
  Studies of Past and Present Maritime Cultures in the Indo-Pacific region}.
  A.A. Balkema, Rotterdam.

\bibitem[Anderson, 2001]{Anderson2001:SharpEnd}
Anderson, A. (2001).
\newblock Towards the sharp end: the form and performance of prehistoric
  polynesian voyaging canoes.
\newblock In Stevenson, C.M., G.~L. and Morin, F., editors, {\em Pacific 2000:
  proceedings of the fifth international conference on Easter Island and the
  Pacific}. Easter Island Foundation, Los Osos.

\bibitem[Anderson et~al., 2000]{Anderson2000:nhst}
Anderson, D.~R., Burnham, K.~P., and Thompson, W.~L. (2000).
\newblock Null hypothesis testing: Problems, prevalence, and an alternative.
\newblock {\em The Journal of Wildlife Management}, 64(4):912--923.

\bibitem[Banack, 1991]{Banack1991ethnobotany}
Banack, S. (1991).
\newblock Plants and polynesian voyaging.
\newblock In Banack, P. A.~C. and Anne, S., editors, {\em Islands, plants, and
  Polynesians : an introduction to Polynesian ethnobotany}. Dioscorides Press,
  Portland, Or.

\bibitem[Barkow et~al., 1992]{Barkow1992adaptedmind}
Barkow, J.~H., Cosmides, L., and Tooby, J. (1992).
\newblock {\em The Adapted Mind: Evolutionary Psychology and the Generation of
  Culture}.
\newblock Oxford University Press.

\bibitem[Baum et~al., 2004]{baum2004cultural}
Baum, W., Richerson, P., Efferson, C., and Paciotti, B. (2004).
\newblock Cultural evolution in laboratory microsocieties including traditions
  of rule giving and rule following.
\newblock {\em Evolution and Human Behavior}, 25(5):305--326.

\bibitem[Begon et~al., 2006]{Begon2006}
Begon, M., Townsend, C.~R., and Harper, J.~L. (2006).
\newblock {\em Ecology}.
\newblock Blackwell Publishing, 4th edition.

\bibitem[Berger and Berry, 1988]{Berger1988}
Berger, J.~O. and Berry, D.~A. (1988).
\newblock Statistical analysis and the illusion of objectivity.
\newblock {\em American Scientist}, 76.

\bibitem[Betzig, 1997]{Betzig1997humannature}
Betzig, L.~L. (1997).
\newblock {\em Human Nature : A Critical Reader}.
\newblock Oxford University Press, New York.

\bibitem[Biggs, 2006]{Biggs2006}
Biggs, B. (2006).
\newblock {\em Kimihia te mea ngaro: Seek that which is lost}.
\newblock The Polynesian Society, Auckland, N.Z.

\bibitem[Bolker, 2008]{Bolker2008}
Bolker, B.~M. (2008).
\newblock {\em Ecological Models and Data in R}.
\newblock Princeton University Press.

\bibitem[Bowles, 2006]{bowles2006microeconomics}
Bowles, S. (2006).
\newblock {\em Microeconomics: Behavior, Institutions, and Evolution}.
\newblock Princeton University Press.

\bibitem[Boyd and Richerson, 1985]{boyd1985culture}
Boyd, R. and Richerson, P. (1985).
\newblock {\em Culture and the Evolutionary Process}.
\newblock University of Chicago Press.

\bibitem[Burnham and Anderson, 2002]{Burnham&Anderson:2002}
Burnham, K. and Anderson, D. (2002).
\newblock {\em Model Selection and Multi-Model Inference: A Practical
  Information-Theoretic Approach}.
\newblock Springer.

\bibitem[Caldwell and Millen, 2008]{caldwell2008studying}
Caldwell, C. and Millen, A. (2008).
\newblock Studying cumulative cultural evolution in the laboratory.
\newblock {\em Philosophical Transactions of the Royal Society B: Biological
  Sciences}, 363(1509):3529.

\bibitem[Campbell, 1965]{campbell1965variation}
Campbell, D. (1965).
\newblock Variation and selective retention in socio-cultural evolution.
\newblock In Barringer, H., Blanksten, G., and Mack, R., editors, {\em Social
  Change in Developing Areas: A Reinterpretation of Evolutionary Theory}, pages
  19--49. Schenkman.

\bibitem[Cashdan and Rogers, 1997]{Cashdan&Rogers1997:review}
Cashdan, E. and Rogers, A. (1997).
\newblock Book review of "human nature: A critical reader".
\newblock {\em Evolution \& Human Behavior}, 18:297--283.

\bibitem[Cavalli-Sforza and Feldman, 1981]{cavalli1981cultural}
Cavalli-Sforza, L. and Feldman, M. (1981).
\newblock {\em Cultural Transmission and Evolution: A Quantitative Approach}.
\newblock Princeton University Press.

\bibitem[Chudek et~al., 2011]{chudek2011prestige}
Chudek, M., Heller, S., Birch, S., and Henrich, J. (2011).
\newblock Prestige-biased cultural learning: Bystander's differential attention
  to potential models influences children's learning.
\newblock {\em Evolution and Human Behavior}.

\bibitem[Cohen, 1994]{Cohen1994}
Cohen, J. (1994).
\newblock The world is round (p $<$ .05).
\newblock {\em American Psychologist}, 49(12):997--1003.

\bibitem[Coulson and Tuljapurkar, 2008]{coulson2008dynamics}
Coulson, T. and Tuljapurkar, S. (2008).
\newblock The dynamics of a quantitative trait in an age-structured population
  living in a variable environment.
\newblock {\em The American Naturalist}, 172(5):599--612.

\bibitem[Dawkins, 2006]{dawkins2006selfish}
Dawkins, R. (2006).
\newblock {\em The Selfish Gene}.
\newblock Oxford University Press.

\bibitem[Diamond, 2002]{Diamond2002domestication}
Diamond, J. (2002).
\newblock Evolution, consequences and future of plant and animal domestication.
\newblock {\em Nature}, 418(6898):700--7.

\bibitem[Doran, 1981]{Doran1981canoes}
Doran, E.~B. (1981).
\newblock {\em Wangka : Austronesian canoe origins}.
\newblock Texas A\&M University Press, College Station, 1st edition.

\bibitem[Durham, 1992]{durham1992coevolution}
Durham, W. (1992).
\newblock {\em Coevolution: Genes, Culture, and Human Diversity}.
\newblock Stanford University Press.

\bibitem[Edgerton, 1971]{Edgerton1971}
Edgerton, R.~B. (1971).
\newblock {\em The individual in cultural adaptation; a study of four East
  African peoples}.
\newblock University of California Press, Berkeley,.

\bibitem[Eerkens et~al., 2006]{EerkensBettingerMcElreath2006}
Eerkens, J.~W., Bettinger, R.~L., and McElreath, R. (2006).
\newblock Cultural transmission, phylogenetics, and the archaeological record.
\newblock In Lipo, C.~P., O'Brien, M.~J., Collard, M., and Shennan, S.~J.,
  editors, {\em Mapping Our Ancestors}. AldineTransactions, London.

\bibitem[Efferson et~al., 2008]{efferson2008conformists}
Efferson, C., Lalive, R., Richerson, P., McElreath, R., and Lubell, M. (2008).
\newblock Conformists and mavericks: The empirics of frequency-dependent
  cultural transmission.
\newblock {\em Evolution and Human Behavior}, 29(1):56--64.

\bibitem[Efferson et~al., 2007a]{efferson2007learning}
Efferson, C., Richerson, P., McElreath, R., Lubell, M., Edsten, E., Waring, T.,
  Paciotti, B., and Baum, W. (2007a).
\newblock Learning, productivity, and noise: An experimental study of cultural
  transmission on the bolivian altiplano.
\newblock {\em Evolution and Human Behavior}, 28(1):11--17.

\bibitem[Efferson et~al., 2007b]{effersontakezawa2007}
Efferson, C., Takezawa, M., and McElreath, R. (2007b).
\newblock New methods in quantitative ethnography: Economic experiments and
  variation in the price of equality.
\newblock {\em Current Anthropology}, 48:912--919.

\bibitem[Eriksson and Coultas, 2009]{eriksson2009people}
Eriksson, K. and Coultas, J. (2009).
\newblock Are people really conformist-biased? an empirical test and a new
  mathematical model.
\newblock {\em Journal of Evolutionary Psychology}, 7(1):5--21.

\bibitem[Fairbairn and Hall, 2009]{Fairbairn2009}
Fairbairn, J. and Hall, T.~M. (2009).
\newblock {\em The Go Companion}.
\newblock Slate and Shell.

\bibitem[Finch, 1994]{Finch1994}
Finch, A. (1994).
\newblock Korean interview.
\newblock {\em British Go Journal}, 96:16--17.

\bibitem[Gaddis, 2002]{Gaddis2002}
Gaddis, J.~L. (2002).
\newblock {\em The Landscape of History: How Historians Map the Past}.
\newblock Oxford University Press.

\bibitem[Gill, 2008]{Gill2008}
Gill, J. (2008).
\newblock {\em Bayesian Methods: A Social and Behavioral Sciences Approach}.
\newblock Chapman \& Hall/CRC, 2nd ed. edition.

\bibitem[Grant and Grant, 2002]{grant2002unpredictable}
Grant, P. and Grant, B. (2002).
\newblock Unpredictable evolution in a 30-year study of darwin's finches.
\newblock {\em Science}, 296(5568):707.

\bibitem[Gravlee et~al., 2009]{gravlee2009methods}
Gravlee, C., Kennedy, D., Godoy, R., and Leonard, W. (2009).
\newblock Methods for collecting panel data: What can cultural anthropology
  learn from other disciplines?
\newblock {\em Journal of Anthropological Research}, 65(3):453--483.

\bibitem[Gray et~al., 2010]{GrayBryantGreenhill2010}
Gray, R., Bryant, D., and Greenhill, S. (2010).
\newblock On the shape and fabric of human history.
\newblock {\em Philosophical Transactions of the Royal Society B: Biological
  Sciences}, 365(1559):3923--3933.

\bibitem[Gray et~al., 2009]{Gray2009:Phylogenies}
Gray, R., Drummond, A., and Greenhill, S. (2009).
\newblock Language phylogenies reveal expansion pulses and pauses in pacific
  settlement.
\newblock {\em Science}, 323.

\bibitem[Guglielmino et~al., 1995]{Guglielmino1995}
Guglielmino, C.~R., Viganotti, C., Hewlett, B., and Cavalli-Sforza, L.~L.
  (1995).
\newblock Cultural variation in africa: Role of mechanisms of transmission and
  adaptation.
\newblock {\em Proceedings of the National Academy of Sciences of the United
  States of America}, 92(16):7585--7589.

\bibitem[Haddon and Hornell, 1936]{HaddonHornell1936}
Haddon, A.~C. and Hornell, J. (1936).
\newblock {\em Canoes of Oceania}.
\newblock Bernice P. Bishop Museum, Honolulu.

\bibitem[Harris, 1968]{Harris1968}
Harris, M. (1968).
\newblock {\em The rise of anthropological theory: a history of theories of
  culture}.
\newblock Routeledge and Kegan Paul Ltd.

\bibitem[Henrich, 2001]{Henrich2001}
Henrich, J. (2001).
\newblock Cultural transmission and the diffusion of innovations: Adoption
  dynamics indicate that biased cultural transmission is the predominate force
  in behavioral change.
\newblock {\em American Anthropologist}, 103(4):992--1013.

\bibitem[Henrich, 2004]{Henrich2004:Tasmania}
Henrich, J. (2004).
\newblock Demography and cultural evolution: How adaptive cultural processes
  can produce maladaptive losses - the tasmanian case.
\newblock {\em American Antiquity}, 69(2).

\bibitem[Henrich and Boyd, 2002]{Henrich2002}
Henrich, J. and Boyd, R. (2002).
\newblock On modeling cognition and culture: Why cultural evolution does not
  require replication of representations.
\newblock {\em Journal of Cognition and Culture}, 2(2):87--112.

\bibitem[Henrich et~al., 2008]{Henrich2008:misunderstandings}
Henrich, J., Boyd, R., and Richerson, P.~J. (2008).
\newblock Five misunderstandings about cultural evolution.
\newblock {\em Human Nature-an Interdisciplinary Biosocial Perspective},
  19(2):119--137.

\bibitem[Henrich and Broesch, 2011]{henrich2011nature}
Henrich, J. and Broesch, J. (2011).
\newblock On the nature of cultural transmission networks: Evidence from fijian
  villages for adaptive learning biases.
\newblock {\em Philosophical Transactions of the Royal Society B: Biological
  Sciences}, 366(1567):1139--1148.

\bibitem[Henrich et~al., 2010]{henrich2010weirdest}
Henrich, J., Heine, S., and Norenzayan, A. (2010).
\newblock The weirdest people in the world?
\newblock {\em Behavioral and Brain Sciences}, 33(2-3):61--83.

\bibitem[Henrich and Henrich, 2010]{henrich2010evolution}
Henrich, J. and Henrich, N. (2010).
\newblock The evolution of cultural adaptations: Fijian food taboos protect
  against dangerous marine toxins.
\newblock {\em Proceedings of the Royal Society B: Biological Sciences},
  277(1701):3715--3724.

\bibitem[Hilborn and Mangel, 1997]{Hilborn1997}
Hilborn, R. and Mangel, M. (1997).
\newblock {\em The ecological detective: confronting models with data}.
\newblock Princeton University Press.

\bibitem[Horridge, 1987]{Horridge1987:IndonesiaCanoes}
Horridge, G.~A. (1987).
\newblock {\em Outrigger canoes of Bali and Madura, Indonesia}.
\newblock Bishop Museum Press, Honolulu.

\bibitem[Hout et~al., 2001]{hout2001demographic}
Hout, M., Greeley, A., and Wilde, M. (2001).
\newblock The demographic imperative in religious change in the united states.
\newblock {\em American Journal of Sociology}, 107(2):468--500.

\bibitem[Irwin, 1992]{Irwin1992}
Irwin, G. (1992).
\newblock {\em The Prehistoric exploration and colonization of the Pacific}.
\newblock Cambridge University Press, Cambridge.

\bibitem[Johnson and Earle, 2000]{JohnsonEarle2000:EvolSocieties}
Johnson, A.~W. and Earle, T.~K. (2000).
\newblock {\em The evolution of human societies : from foraging group to
  agrarian state}.
\newblock Stanford University Press, Stanford, Calif., 2nd edition.

\bibitem[Johnson and Omland, 2004]{Johnson&Omland2004:modelselection}
Johnson, J.~B. and Omland, K.~S. (2004).
\newblock Model selection in ecology and evolution.
\newblock {\em Trends in Ecology \& Evolution}, 19(2):101--108.

\bibitem[Kirch, 1984]{Kirch1984evolution}
Kirch, P.~V. (1984).
\newblock {\em The evolution of the Polynesian chiefdoms}.
\newblock New studies in archaeology. Cambridge University Press, Cambridge.

\bibitem[Kirch, 2000]{Kirch2000:Road}
Kirch, P.~V. (2000).
\newblock {\em On the road of the winds : an archaeological history of the
  Pacific Islands before European contact}.
\newblock University of California Press, Berkeley, Calif.

\bibitem[Kirch, 2007]{Kirch2007}
Kirch, P.~V. (2007).
\newblock Hawaii as a model system for human ecodynamics.
\newblock {\em American Anthropologist}, 109(1):8--26.

\bibitem[Laland and Brown, 2002]{LalandBrown2002sense}
Laland, K.~N. and Brown, G.~R. (2002).
\newblock {\em Sense and nonsense: Evolutionary perspectives on human
  behaviour}.
\newblock Oxford University Press, New York.

\bibitem[Lewis, 1978]{Lewis1978:PacificNavigators}
Lewis, D. (1978).
\newblock {\em The voyaging stars : secrets of the Pacific island navigators}.
\newblock W. W. Norton, New York.

\bibitem[Lumsden and Wilson, 2005]{lumsden2005genes}
Lumsden, C. and Wilson, E. (2005).
\newblock {\em Genes, Mind, and Culture: The Coevolutionary Process}.
\newblock World Scientific Publishing Company.

\bibitem[McElreath, 2004]{mcelreath2004social}
McElreath, R. (2004).
\newblock Social learning and the maintenance of cultural variation: An
  evolutionary model and data from east africa.
\newblock {\em American Anthropologist}, 106(2):308--321.

\bibitem[McElreath et~al., 2008]{mcelreath2008beyond}
McElreath, R., Bell, A., Efferson, C., Lubell, M., Richerson, P., and Waring,
  T. (2008).
\newblock Beyond existence and aiming outside the laboratory: Estimating
  frequency-dependent and payoff-biased social learning strategies.
\newblock {\em Philosophical Transactions of the Royal Society B: Biological
  Sciences}, 363(1509):3515--3528.

\bibitem[McElreath et~al., 2005]{mcelreath2005applying}
McElreath, R., Lubell, M., Richerson, P., Waring, T., Baum, W., Edsten, E.,
  Efferson, C., and Paciotti, B. (2005).
\newblock Applying evolutionary models to the laboratory study of social
  learning.
\newblock {\em Evolution and Human Behavior}, 26(6):483--508.

\bibitem[Mead, 1957]{Mead1957:PolynesianLab}
Mead, M. (1957).
\newblock Introduction to polynesia as laboratory for the development of models
  in the study of cultural evolution.
\newblock {\em Journal of the Polynesian Society}, 66:145.

\bibitem[Mesoudi, 2011]{Mesoudi2011a}
Mesoudi, A. (2011).
\newblock An experimental comparison of human social learning strategies:
  payoff-biased social learning is adaptive but underused.
\newblock {\em Evolution and Human Behavior}, 32(5):334--342.

\bibitem[Mesoudi and O'Brien, 2008]{mesoudi2008cultural}
Mesoudi, A. and O'Brien, M. (2008).
\newblock The cultural transmission of great basin projectile-point technology
  i: An experimental simulation.
\newblock {\em American Antiquity}, pages 3--28.

\bibitem[Mesoudi et~al., 2006]{Mesoudi2006}
Mesoudi, A., Whiten, A., and Laland, K.~N. (2006).
\newblock Towards a unified science of cultural evolution.
\newblock {\em Behavioral and Brain}, 29:329--383.

\bibitem[Michel et~al., 2011]{michel2011quantitative}
Michel, J., Shen, Y., Aiden, A., Veres, A., Gray, M., Pickett, J., Hoiberg, D.,
  Clancy, D., Norvig, P., and Orwant, J. (2011).
\newblock Quantitative analysis of culture using millions of digitized books.
\newblock {\em Science}, 331(6014):176.

\bibitem[Mueller-Dombois and Fosberg, 1998]{Mueller1998:Vegetation}
Mueller-Dombois, D. and Fosberg, F.~R. (1998).
\newblock {\em Vegetation of the tropical Pacific islands}.
\newblock Springer, New York.

\bibitem[Nisbett and Cohen, 1996]{Nisbett1996}
Nisbett, R.~E. and Cohen, D. (1996).
\newblock {\em Culture of honor: the psychology of violence in the South}.
\newblock New directions in social psychology. Westview Press, Boulder, CO.

\bibitem[Ozgul et~al., 2009]{ozgul2009dynamics}
Ozgul, A., Tuljapurkar, S., Benton, T., Pemberton, J., Clutton-Brock, T., and
  Coulson, T. (2009).
\newblock The dynamics of phenotypic change and the shrinking sheep of st.
  kilda.
\newblock {\em Science}, 325(5939):464.

\bibitem[Paciotti and Hadley, 2003]{paciotti2003ultimatum}
Paciotti, B. and Hadley, C. (2003).
\newblock The ultimatum game among sympatric ethnic groups in southwestern
  tanzania: Ethnic variation and institutional scope.
\newblock {\em Current Anthropology}, 44:427--432.

\bibitem[Price, 1970]{price1970selection}
Price, G.~R. (1970).
\newblock Selection and covariance.
\newblock {\em Nature}, 227(5257):520--521.

\bibitem[Rendell et~al., 2011]{rendell2011copying}
Rendell, L., Boyd, R., Enquist, M., Feldman, M., Fogarty, L., and Laland, K.
  (2011).
\newblock How copying affects the amount, evenness and persistence of cultural
  knowledge: insights from the social learning strategies tournament.
\newblock {\em Philosophical Transactions of the Royal Society B: Biological
  Sciences}, 366(1567):1118--1128.

\bibitem[Rice, 2004]{rice2004evolutionary}
Rice, S. (2004).
\newblock {\em Evolutionary Theory: Mathematical and Conceptual Foundations}.
\newblock Sinauer Associates Sunderland.

\bibitem[Richerson and Boyd, 2005]{Richerson2005:NBGA}
Richerson, P. and Boyd, R. (2005).
\newblock {\em Not by Genes Alone: How Culture Transformed Human Evolution}.
\newblock University of Chicago Press.

\bibitem[Rimmel et~al., 2010]{Rimmel2010}
Rimmel, A., Teytaud, O., Lee, C.-S., Yen, S.-J., Wang, M.-H., and Tsai, S.-R.
  (2010).
\newblock Current frontiers in computer go.
\newblock {\em Computational Intelligence and AI in Games, IEEE Transactions
  on}, 2(4):229 --238.

\bibitem[Rogers and Cashdan, 1997]{Rogers&Cashdan1997:phylogeny}
Rogers, A. and Cashdan, E. (1997).
\newblock The phylogenetic approach to comparing human populations.
\newblock {\em Evolution \& Human Behavior}, 18(5):353--358.

\bibitem[Rogers et~al., 2009]{RogersFeldmanEhrlich2009}
Rogers, D., Feldman, M., and Ehr (2009).
\newblock Inferring population histories using cultural data.
\newblock {\em Proceedings of the Royal Society B: Biological Sciences},
  276(1674):3835--3843.

\bibitem[Rogers and Ehrlich, 2008]{Rogers2008:Canoes}
Rogers, D.~S. and Ehrlich, P.~R. (2008).
\newblock Natural selection and cultural rates of change.
\newblock {\em Proceedings of the National Academy of Sciences of the United
  States of America}, 105(9):3416--3420.

\bibitem[Sahlins, 1976]{Sahlins1976:critiqueSociobiology}
Sahlins, M.~D. (1976).
\newblock {\em The use and abuse of biology : an anthropological critique of
  sociobiology}.
\newblock University of Michigan Press, Ann Arbor.

\bibitem[Segoe, 1960]{Segoe1960}
Segoe, K. (1960).
\newblock {\em Go Proverbs Illustrated}.
\newblock Nihon Ki-In.

\bibitem[Shennan, 2009]{Shennan2009}
Shennan, S., editor (2009).
\newblock {\em Pattern and Process in Cultural Evolution}.
\newblock University of California Press.

\bibitem[Shotwell, 2003]{Shotwell2003}
Shotwell, P. (2003).
\newblock {\em Go! More than a game}.
\newblock Tuttle Publishing.

\bibitem[Skoyles, 2008]{Skoyles2008:canoechange}
Skoyles, J.~R. (2008).
\newblock Natural selection does not explain cultural rates of change.
\newblock {\em Proceedings of the National Academy of Sciences of the United
  States of America}, 105(22).

\bibitem[Spiegelhalter et~al., 2002]{Spiegelhalter2002}
Spiegelhalter, D.~J., Best, N.~G., Carlin, B.~P., and Linde, A. v.~d. (2002).
\newblock Bayesian measures of model complexity and fit.
\newblock {\em Journal Of The Royal Statistical Society Series B},
  64(4):583--639.

\bibitem[Stark, 1996]{stark1996rise}
Stark, R. (1996).
\newblock {\em The Rise of Christianity: A Sociologist Reconsiders History}.
\newblock Princeton University Press.

\bibitem[Steward, 1955]{Steward1955}
Steward, J.~H. (1955).
\newblock {\em Theory of Cultural Change: The Methodology of Multilinear
  Evolution}.
\newblock University of Illinois Press, Urbana.

\bibitem[Temkin and Eldredge, 2007]{Temkin2007:CulturePhylogenetics}
Temkin, I. and Eldredge, N. (2007).
\newblock Phylogenetics and material cultural evolution.
\newblock {\em Current Anthropology}, 48(1):146--153.

\bibitem[Thomas, 2008]{Thomas2008:Lastpulse}
Thomas, T. (2008).
\newblock The long pause and the last pulse: Mapping east polynesian
  colonisation.
\newblock In Clark, Geoffry, F.~L. and O'Connor, S., editors, {\em Islands of
  Inquiry: Colonisation, seafaring and the archaeology of maritime landscapes}.
  ANU E press.

\bibitem[Weisler, 1998]{Weisler1998}
Weisler, M.~I. (1998).
\newblock Hard evidence for prehistoric interaction in polynesia.
\newblock {\em Current Anthropology}, 39(4):521--532.

\bibitem[Whyte et~al., 2005]{Whyte2005:PolyHumanEvol}
Whyte, A. L.~H., Marshall, S.~J., and Chambers, G.~K. (2005).
\newblock Human evolution in polynesia.
\newblock {\em Human Biology}, 77(2):157--177.

\bibitem[Wimsatt and Griesemer, 2007]{Wimsatt2007}
Wimsatt, W.~C. and Griesemer, J.~R. (2007).
\newblock {\em Integrating evolution and development: from theory to practice},
  chapter Reproducing Entrenchments to Scaffold Culture: The Central Role of
  Development in Cultural Evolution.
\newblock MIT Press.

\bibitem[Winterhalder and Smith, 2000]{WinterhalderSmith2000}
Winterhalder, B. and Smith, E.~A. (2000).
\newblock Analyzing adaptive strategies: Human behavioral ecology at
  twenty-five.
\newblock {\em Evolutionary Anthropology: Issues, News, and Reviews},
  9(2):51--72.

